---
output:
  pdf_document:
    includes:
      in_header: styles.tex
    number_sections: TRUE
    latex_engine: xelatex
    fig_caption: yes
    fig_width: 4
    fig_height: 3
    keep_tex: TRUE
header-includes:
  - \usepackage{titling}
  - \setlength{\droptitle}{5em} 
papersize: a4paper
fontsize: 11pt
mainfont: Calibri
geometry: margin = 3cm
subparagraph: TRUE
graphics: yes
bibliography: References.bib
csl: apa.csl
link-citations: yes
params:
  mainFile: "DEMO DATA R9/ESS10 DATA_MAIN_QUESTIONNAIRE_TIMESTAMPS.sav"
  intFile: "DEMO DATA R9/ESS10 DATA_INTERVIEWER QUESTIONNAIRE.sav"

# European Social Survey - European Research Infrastructure (ESS-ERIC)
# europeansocialsurvey.org
# Notes
# Version: 6.2 data structure inspection
# Data format: SPSS
---

```{r setup, include = FALSE, error=T}
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = TRUE, results = "show", message = FALSE, dev = "cairo_pdf", warning = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')

options(knitr.table.format = "latex", knitr.kable.NA = "")

Sys.setlocale("LC_ALL","English")
```

```{r setup2, include = FALSE, error=T}
#Installed packages
library(here) 
library(foreign)
library(dplyr)
library(psych)
library(ggplot2)
library(lubridate)
library(wesanderson)
library(haven)
library(colortools) # adjacent works
library(ggthemes) # theme_tufte works
library(varhandle) # coercing factor to numeric variables
library(naniar) # for replacing values with missings
library(knitr)
library(kableExtra)
library("Gifi") #Implements categorical principal component analysis
library(matrixStats) #High-performing functions operating on rows and columns of matrices
library(cowplot)
library(tibble)

#Utilities
source("Utility functions.R")
linebreak <- "\\hspace{\\textwidth}"
```

```{r theme, include = FALSE, error=T}
ESSred <- rgb(.91, .20, .32)
ESSgreen <- rgb(.14, .62, .51)
ESSblue <- rgb(0, .25, .48)
  
ESSColors <- unique(c(adjacent(ESSred, plot = F), square(ESSred, plot = F)))

ESSColors <- c(ESSColors, ESSgreen, ESSblue)
# pizza(ESSColors)

themeESS <- theme_tufte(base_size = 9, base_family = "Calibri") +
    theme(axis.title = element_text(size = 9, face = "plain"),
          axis.text = element_text(size = 9),
          axis.line.x = element_line(),
          plot.title = element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size = 9),
          strip.text = element_text(size = 9, face = "bold"),
          legend.position = "none",
          legend.direction = "horizontal",
          legend.box = "vertical",
          legend.spacing = unit(0, "line"),
          legend.key.size = unit(.75, "line"))
linebreak <- "\\hspace{\\textwidth}"
```

\newpage
\FloatBarrier
\pagenumbering{gobble}

\pagenumbering{arabic}

\setcounter{tocdepth}{2}

# Inspection Data Structure {-}

```{r getdata, error=T}
# Interviewer-Questionnaire with Inwer ID (intnum):
Inwer <- foreign::read.spss(params$intFile,
                 use.value.labels = F,
                 use.missings = F,
                 to.data.frame = T)
# Main Dataset
Main <- foreign::read.spss(params$mainFile,
                 use.value.labels = F,
                 use.missings = F,
                 to.data.frame = T)

# Inwer<-haven::read_spss(params$intFile)
# Main<-haven::read_spss(params$mainFile)

#Variable names to lower cases
names(Inwer) <- tolower(names(Inwer))
names(Main) <- tolower(names(Main))
Inwer_ID <- dplyr::select(Inwer, "intnum", "idno")
Main <- dplyr::left_join(Main, Inwer_ID, by = "idno")
```

```{r countrynames_rounds, error=T}
# this Country
Countrynames <- (read.csv2("Country names and codes.csv", dec = ".", stringsAsFactors = F))
Country <- as.data.frame(Main$cntry)
Country <- dplyr::rename(Country, cntry = 'Main$cntry')
Country <- left_join(Country, Countrynames, by = "cntry")
thisCountry <- unique(Country$CountryName)
```

```{r missingintnum, error=T}
# Allcases in Main
Mainfull <- Main
# Filter out cases without intnum
Main <- Main %>% filter(!is.na(intnum))
```

This report presents the results of inspection of the data structure of interim dataset in `r thisCountry`. It is aimed to solve issues in the implementation of the tool. If you are having problems with the implemenation of the tool, please share this report with your Country Contact or the ESS Team for Desirable Interviewer Behaviour via my ESS.
The data provided contained a total of `r length(Mainfull$idno)` cases. A total of `r length(Main$idno)` cases had a valid interviewer number.


# Data Structure and Variable Characteristic {#sec:datastructure}

```{r data check, error=T}

#Var check
print(names(Mainfull)) #selected maim dataset prior merge
print(names(Inwer)) #selected iwer dataset prior merge
names(Country)

#Variable class
sapply(Main, class) #merged dataset

#NAs in key variables?
table(is.na(Main$cntry))
table(is.na(Main$idno))
table(is.na(Main$intnum))

#Unique idno
length(unique(Main$idno))

#Print cntry
table(Main$cntry)
table(Inwer$cntry)
table(Country$cntry)

#Cases per iwer
Main %>% group_by(intnum) %>%
  summarise(nperm = n())

#Data structure 
psych::describe(Main) #n, mean, sd, median, min, max, range, etc. 
sapply(Main, mean, na.rm=FALSE)

#Query locales
Sys.setlocale()
Sys.Date()

```