---
output:
  pdf_document:
    includes:
      in_header: styles.tex
    number_sections: TRUE
    latex_engine: xelatex
    fig_caption: yes
    fig_width: 4
    fig_height: 3
    keep_tex: TRUE
header-includes:
  - \usepackage{titling}
  - \setlength{\droptitle}{5em} 
papersize: a4paper
fontsize: 11pt
mainfont: Calibri
geometry: margin = 3cm
subparagraph: TRUE
graphics: yes
bibliography: References.bib
csl: apa.csl
link-citations: yes
params:
  mainFile: ""
  intFile: ""

# European Social Survey - European Research Infrastructure (ESS-ERIC)
# europeansocialsurvey.org
# Notes
# Version: 6.0 data structure inspection
# Data format: SAS
---

```{r setup, include = FALSE, error=T}
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = TRUE, results = "show", message = FALSE, dev = "cairo_pdf", warning = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')

options(knitr.table.format = "latex", knitr.kable.NA = "")

Sys.setlocale("LC_ALL","English")
```

```{r setup2, include = FALSE, error=T}
#Installed packages
library(here) 
library(foreign)
library(dplyr)
library(psych)
library(ggplot2)
library(lubridate)
library(wesanderson)
library(colortools) # adjacent works
library(ggthemes) # theme_tufte works
library(varhandle) # coercing factor to numeric variables
library(naniar) # for replacing values with missings
library(knitr)
library(kableExtra)
library("Gifi") #Implements categorical principal component analysis
library(matrixStats) #High-performing functions operating on rows and columns of matrices
library(cowplot)
library(tibble)

#Utilities
source("Utility functions.R")
linebreak <- "\\hspace{\\textwidth}"
```

```{r theme, include = FALSE, error=T}
ESSred <- rgb(.91, .20, .32)
ESSgreen <- rgb(.14, .62, .51)
ESSblue <- rgb(0, .25, .48)
  
ESSColors <- unique(c(adjacent(ESSred, plot = F), square(ESSred, plot = F)))

ESSColors <- c(ESSColors, ESSgreen, ESSblue)
# pizza(ESSColors)

themeESS <- theme_tufte(base_size = 9, base_family = "Calibri") +
    theme(axis.title = element_text(size = 9, face = "plain"),
          axis.text = element_text(size = 9),
          axis.line.x = element_line(),
          plot.title = element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size = 9),
          strip.text = element_text(size = 9, face = "bold"),
          legend.position = "none",
          legend.direction = "horizontal",
          legend.box = "vertical",
          legend.spacing = unit(0, "line"),
          legend.key.size = unit(.75, "line"))
linebreak <- "\\hspace{\\textwidth}"
```

\newpage
\FloatBarrier
\pagenumbering{gobble}

```{r child = "Titlepage.Rmd", error=T}
```

\pagenumbering{arabic}

\setcounter{tocdepth}{2}
\tableofcontents
\listoftables
\listoffigures

# Introduction {-}

```{r getdata, error=T}
# Interviewer-Questionnaire with Inwer ID (intnum):
Inwer <- haven::read_sas(params$intFile)

# Main Dataset
Main <- haven::read_sas(params$mainFile)

#Variable names to lower cases
names(Inwer) <- tolower(names(Inwer))
names(Main) <- tolower(names(Main))

Inwer_ID <- dplyr::select(Inwer, "intnum", "idno")
Main <- dplyr::left_join(Main, Inwer_ID, by = "idno")
```

```{r countrynames_rounds, error=T}
# this Country
Countrynames <- (read.csv2("Country names and codes.csv", dec = ".", stringsAsFactors = F))
Country <- as.data.frame(Main$cntry)
Country <- dplyr::rename(Country, cntry = 'Main$cntry')
Country <- left_join(Country, Countrynames, by = "cntry")

thisCountry <- unique(Country$CountryName)
```

```{r missingintnum, error=T}
# Allcases in Main
Mainfull <- Main

# Filter out cases without intnum
Main <- Main %>% filter(!is.na(intnum))
```

This report presents the results of the analysis of the interim dataset for `r thisCountry`. It aims to help national teams detecting undesirable interviewer behaviour. The report is divided into three sections. The first section presents the results on the analysis of the timestamps from the interview. The second section focuses on item non-response. The third section investigates response patterns of respondents and how these related to allocations within interviewers. Guidance as to how to interpret these results is also provided. 

It is recommended to  view these indicators as complementary to the information coming from the field. They help gain further insights into activities in the field. Indicators are complementary to each other as well.

It should also be noted that the analysis focused only on cases that have a valid interviewer number as it is assumed that all interviews have been conducted by an interviewer. Therefore, any case missing the interviewer number are not included in the analysis. The data provided to the tool contained a total of `r length(Mainfull$idno)` cases and a total of `r length(Main$idno)` contained a valid interviewer number.

Please feel free to contact your Country Contact or the ESS DIB team via myESS if you have any questions.


# Interview timestamps {#sec:timestamps}

```{r data check, error=T}

#Var check
print(names(Main))
print(names(Inwer))
names(Country)

#NAs in key variables?
table(is.na(Main$cntry))
table(is.na(Main$idno))
table(is.na(Main$intnum))

#Print cntry
table(Main$cntry)
table(Inwer$cntry)
table(Country$cntry)

#Data structure 
sapply(Main, mean, na.rm=FALSE)
describe(Main)

#Query locales
Sys.setlocale()
Sys.Date()

```